---
title: "Statistical Inference Project"
author: "Ahsan Habib Sunny"
date: "7/14/2020"
output: pdf_document
editor_options: 
  chunk_output_type: inline
---

# Comparison betweeen theoretical average and calculated sample average.

```{r}
set.seed(4085)
n<- 40
Simulation<- 1000
lambda<- 0.2

samplemean <- NULL

for(i in 1:Simulation) {
  samplemean <-c(samplemean, mean(rexp(n, lambda)))
}
mean(samplemean)

```
#### so, as we can see that our theoretical exponential mean is 1/0.2=5 and our calculated sample mean is close to 5 which is 5.012

# Comparison betweeen theoretical variance and calculated.

```{r}
variance <- var(samplemean)

variance

```
#### our calculated variance is 0.66 whereas the theoretical variance is the square of theoretical sd which is (1/0.2)^2=25.

# Show whether the distribution is normal or not.

```{r}
hist(samplemean, breaks = n, prob = T, col = "blue", xlab = "Means")
x <- seq(min(samplemean), max(samplemean), length = 100)
lines(x,dnorm(x,1/lambda,(1/lambda/sqrt(n))),col="green")

```
*The distribution averages of 40 exponentials is very close to a normal distribution*



